
# **Intro to Predictive Modeling Exercise 1- Anuraag Mohile**

## Probability Practice
### Part A.
Let Y->Yes, T->Truthful Clicker, R->Random Clicker

P(T)= 0.7, P(R)=0.3, P(Y|R)=0.5, P(Y)=0.65


According to the rule of total probability,

P(Y)=P(Y|T).P(T) + P(Y|R).P(R)

0.65=P(Y|T).0.7 + 0.5.0.3

P(Y|T)=5/7


### Part B.
Let, A-> Test is positive, B-> Has disease

P(A|B)=0.993

P(not A| not B)=0.9999 <=> P(A|not B)=0.0001

P(B)=0.000025 <=> P(not B)=0.999975


According to the rule of total probability,

P(A)=P(A|B).P(B) + P(A|not B).P(not B)

P(A)=0.993.0.000025 + 0.0001.0.999975

P(A)=0.000124822

According to Baye's Theorem,

P(B|A)=P(A|B).P(B)/P(A)

P(B|A)=0.993.0.000025/0.000124822

P(B|A)=0.19888 ~ 20%


Thus, the test would be wrong 80% of the time when the result is positive.


## Exploratory analysis: green buildings

Let us first split the dataset into subsets of green-rated and not green-rated
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
g=read.csv("greenbuildings.csv")
green=g[g$green_rating==1,]
no_green=g[g$green_rating==0,]
```
Now, let's see the ages for each




```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
plot(green$age)
```




Median age for green-rated buildings:
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
median(green$age)
```
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
plot(no_green$age)
```




Median age for normal buildings:
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
median(no_green$age)
```
We see that green-rated buildings tend to be newer.
Now, let's see the relationship between age and rent
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
f=g[g$Rent<75,]
plot(f$age,f$Rent)
```






We see that newer buildings tend to have higher rents. Exploring this further:

Median rent for houses below 30 years old:
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
median(g[g$age<30,]$Rent)
```
Median rent for houses above 30 years old:
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
median(g[g$age>30,]$Rent)
```
Thus, the difference in rents that the Excel guru got, could be explained by the age of the buildings, among other "behind-the-scenes" variables. 
The "stats guru"" forgot that correlation doesn't mean causation.
We need to look at more variables which could be correlated with green-rating, and could be responsible for the rent difference, before drawing conclusions about whether building a green-rated building is viable or not. If other variables are controlled, we can get a clearer idea on that matter.


## **Bootstrapping**
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
set.seed(7)
library(mosaic)
library(quantmod)
library(foreach)
```
### One Asset at a time
#### Only TLT in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#One at a time
#TLT
set.seed(7)
mystocks = c("TLT")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind 'a' to the end
for(ticker in mystocks) {
    expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
    eval(parse(text=expr))
}



# Combine all the returns in a matrix
all_returns = cbind(ClCl(TLTa))
all_returns = as.matrix(na.omit(all_returns))


# simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
    total_wealth = initial_wealth
    weights = c(1)
    holdings = weights * total_wealth
    n_days = 20
    wealthtracker = rep(0, n_days)
    for(today in 1:n_days) {
        return.today = resample(all_returns, 1, orig.ids=FALSE)
        holdings = holdings + holdings*return.today
        total_wealth = sum(holdings)
        wealthtracker[today] = total_wealth
    }
    wealthtracker
}
```
Total wealth if only TLT in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
```
5% VAR if only TLT in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
```
#### Only SPY in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#One at a time
#SPY
set.seed(7)
mystocks = c("SPY")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind 'a' to the end

for(ticker in mystocks) {
    expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
    eval(parse(text=expr))
}



# Combine all the returns in a matrix
all_returns = cbind(ClCl(SPYa))
all_returns = as.matrix(na.omit(all_returns))


# simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
    total_wealth = initial_wealth
    weights = c(1)
    holdings = weights * total_wealth
    n_days = 20
    wealthtracker = rep(0, n_days)
    for(today in 1:n_days) {
        return.today = resample(all_returns, 1, orig.ids=FALSE)
        holdings = holdings + holdings*return.today
        total_wealth = sum(holdings)
        wealthtracker[today] = total_wealth
    }
    wealthtracker
}
```
Total wealth if only SPY in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
```
5% VAR if only SPY in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
```
#### Only LQD in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#One at a time
#LQD
set.seed(7)
mystocks = c("LQD")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind 'a' to the end

for(ticker in mystocks) {
    expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
    eval(parse(text=expr))
}



# Combine all the returns in a matrix
all_returns = cbind(ClCl(LQDa))
all_returns = as.matrix(na.omit(all_returns))


# simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
    total_wealth = initial_wealth
    weights = c(1)
    holdings = weights * total_wealth
    n_days = 20
    wealthtracker = rep(0, n_days)
    for(today in 1:n_days) {
        return.today = resample(all_returns, 1, orig.ids=FALSE)
        holdings = holdings + holdings*return.today
        total_wealth = sum(holdings)
        wealthtracker[today] = total_wealth
    }
    wealthtracker
}
```
Total wealth if only LQD in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
```
5% VAR if only LQD in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
```
#### Only EEM in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#One at a time
#EEM
set.seed(7)
mystocks = c("EEM")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind 'a' to the end

for(ticker in mystocks) {
    expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
    eval(parse(text=expr))
}



# Combine all the returns in a matrix
all_returns = cbind(ClCl(EEMa))
all_returns = as.matrix(na.omit(all_returns))


# simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
    total_wealth = initial_wealth
    weights = c(1)
    holdings = weights * total_wealth
    n_days = 20
    wealthtracker = rep(0, n_days)
    for(today in 1:n_days) {
        return.today = resample(all_returns, 1, orig.ids=FALSE)
        holdings = holdings + holdings*return.today
        total_wealth = sum(holdings)
        wealthtracker[today] = total_wealth
    }
    wealthtracker
}
```
Total wealth if only EEM in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
```
5% VAR if only EEM in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
```
#### Only VNQ in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#One at a time
#VNQ
set.seed(7)
mystocks = c("VNQ")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind 'a' to the end

for(ticker in mystocks) {
    expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
    eval(parse(text=expr))
}



# Combine all the returns in a matrix
all_returns = cbind(ClCl(VNQa))
all_returns = as.matrix(na.omit(all_returns))


# simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
    total_wealth = initial_wealth
    weights = c(1)
    holdings = weights * total_wealth
    n_days = 20
    wealthtracker = rep(0, n_days)
    for(today in 1:n_days) {
        return.today = resample(all_returns, 1, orig.ids=FALSE)
        holdings = holdings + holdings*return.today
        total_wealth = sum(holdings)
        wealthtracker[today] = total_wealth
    }
    wealthtracker
}
```
Total wealth if only VNQ in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
```
5% VAR if only VNQ in portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
```
We see that LQD has lowest risk but also gives lowest profit; TLT has double the risk but not much more profit than LQD; SPY is riskier than both of them, but has higher profits; EEM has considerably higher profits and not too high a risk considering the profits, but it is higher than even SPY; VNQ seems to be the worst since, the profit is only marginally higher than SPY but risk is almost double, and highest out of the lot.


### *Even Split Portfolio*
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#Import a few stocks

mystocks = c("TLT", "LQD", "SPY", "VNQ", "EEM")
getSymbols(mystocks)


#Adjust for splits and dividends

TLTa = adjustOHLC(TLT)
LQDa = adjustOHLC(LQD)
SPYa = adjustOHLC(SPY)
VNQa = adjustOHLC(VNQ)
EEMa = adjustOHLC(EEM)


#Combine close to close changes in a single matrix

all_returns = cbind(ClCl(TLTa),ClCl(LQDa),ClCl(SPYa),ClCl(VNQa),ClCl(EEMa))
all_returns = as.matrix(na.omit(all_returns))

```
Correlation matrix for the 5 assets
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
#The sample correlation matrix

cor(all_returns)



#### Now use a bootstrap approach
set.seed(7)

mystocks = c("SPY", "TLT", "LQD", "VNQ", "EEM")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind a to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}


# Combine all the returns in a matrix
all_returns = cbind(	ClCl(SPYa),
								ClCl(TLTa),
								ClCl(LQDa),
								ClCl(VNQa),
								ClCl(EEMa))

all_returns = as.matrix(na.omit(all_returns))

# Now simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.2, 0.2, 0.2, 0.2, 0.2)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}

hist(sim1[,n_days], 25)
```





Total wealth for even split portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
```



5% VAR for even split portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
 
```
### *Safer Portfolio*

To make a safer portfolio, we need to consider the assets with lower risks. Also, at least 2 assets need to be negatively correlated since, if one of them goes down, the other one shouldn't go down too because of it.
Keeping this in mind, we see that LQD, TLT, and SPY seem to be the best. They have the lowest risks out of the 5. Also, TLT and SPY are negatively correlated.
Allocations: 50% for LQD, 30% for SPY, 20% for TLT
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
set.seed(7)
mystocks = c("SPY", "TLT", "LQD")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind a to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}


# Combine all the returns in a matrix
all_returns = cbind(	ClCl(SPYa),
								ClCl(TLTa),
								ClCl(LQDa))

all_returns = as.matrix(na.omit(all_returns))

# Now simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.3,0.2,0.5)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}

hist(sim1[,n_days], 25)
```





Total wealth for safer portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
```



5% VAR for safer portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
 
```
### *Aggressive Portfolio*

EEM has highest profit along with a high risk. It has the best Profit to Risk ratio. So adding another asset which lowers the risk while not decreasing the profit too much is what's required. TLT works best since, it is the only one negatively correlated with EEM.
Allocation: 60% to EEM; 40% to TLT
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
set.seed(7)
mystocks = c("EEM", "TLT")
myprices = getSymbols(mystocks, from = "2007-01-01")


# A chunk of code for adjusting all stocks
# creates a new object addind a to the end
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}


# Combine all the returns in a matrix
all_returns = cbind(
								ClCl(EEMa),ClCl(TLTa))

all_returns = as.matrix(na.omit(all_returns))

# Now simulate many different possible scenarios  
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.6,0.4)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}

hist(sim1[,n_days], 25)
```





Total wealth for aggressive portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Profit/loss
mean(sim1[,n_days])
hist(sim1[,n_days]- initial_wealth, breaks=30)
```





5% VAR for aggressive portfolio
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Calculate 5% value at risk
quantile(sim1[,n_days], 0.05) - initial_wealth
 
```

## Market Segmentation

Using PCA:

```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
library(ggplot2)

set.seed(7)

interest_data = read.csv("social_marketing.csv", row.names=1)

# First normalize phrase counts to phrase frequencies.
Z = interest_data/rowSums(interest_data)

# PCA
pc2 = prcomp(Z, scale=TRUE, rank=2)
loadings = pc2$rotation
scores = pc2$x

# Question 1: where do the observations land in PC space?
# a biplot shows the first two PCs
qplot(scores[,1], scores[,2], xlab='Component 1', ylab='Component 2')
```



We see that most of the observations are very closely clustered around the top & top-left, while some are clustered near the bottom (Negative of second PC) and others to the right (Positive of first PC)


The top words associated with each component:

PC1:
Positive side
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
# Question 2: how are the individual PCs loaded on the original variables?
o1 = order(loadings[,1], decreasing=TRUE)
colnames(Z)[head(o1,6)]
```
Negative Side
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
colnames(Z)[tail(o1,6)]
```

PC2:
Positive side
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
o2 = order(loadings[,2], decreasing=TRUE)
colnames(Z)[head(o2,6)]
```
Negative Side
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
colnames(Z)[tail(o2,6)]
```

Graph of variables along with their contributions represented by color
```{r,echo=FALSE,message=FALSE,warning=FALSE,comment=""}
library("FactoMineR")
library("factoextra")
fviz_pca_var(pc2, col.var="contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = FALSE
             )
```


We can see 2 clear clusters- 

1)One which includes "family",school","parenting","food","religion", etc.
These represent more of 'familial', core values.

2)Second which includes "beauty", "fashion", "personal_fitness", "health_nutrition", etc.
These are more of self-care related interests.

